Trends in Death License: Analyzing the Distribution of Death Licenses in Great Toronto Area

### 2024-09-27 Death_License_main_file/paper/paper.qmd
Final upload

mydatapath <- "~/Paper 1/starter_folder-main/data/analysis_data/analysis_data.csv"
data <- read_csv(mydatapath)
```

@@

cleaned_data <- read_csv(here::here("~/Paper 1/starter_folder-main/data/analysis_data/analysis_data.csv"))

@@

data <- read_csv(here::here("~/Paper 1/starter_folder-main/data/analysis_data/analysis_data.csv"))

@@

# Read the CSV file
data <- read_csv(here::here("~/Paper 1/starter_folder-main/data/analysis_data/analysis_data.csv"))

@@

```{r}
#| label: fig-03
#| tbl-cap: "Prediction of Death License in 2024 9-12 "
#| echo: false
#| message: false
#| warning: false
#|
# Read the data
data <- read_csv(here::here("~/Paper 1/starter_folder-main/data/analysis_data/analysis_data.csv"))

>>>>

mydatapath <- "~/Desktop/Death-License-Project/Death_License_main_file/data/analysis_data/analysis_data.csv"
data <- read_csv(mydatapath)
```

@@

cleaned_data <- read_csv(here::here("~/Desktop/Death-License-Project/Death_License_main_file/data/analysis_data/analysis_data.csv"))

@@

data <- read_csv(here::here("~/Desktop/Death-License-Project/Death_License_main_file/data/analysis_data/analysis_data.csv"))

@@

# Read the CSV file
data <- read_csv(here::here("~/Desktop/Death-License-Project/Death_License_main_file/data/analysis_data/analysis_data.csv"))

@@

```{r}
#| label: fig-03
#| tbl-cap: "Prediction of Death License in 2024 9-12 "
#| echo: false
#| message: false
#| warning: false
#|
# Read the data
data <- read_csv(here::here("~/Desktop/Death-License-Project/Death_License_main_file/data/analysis_data/analysis_data.csv"))
